---
title: "Cox’s Bazar Rohingya Camps - Epidemiological Summary"
output:
  word_document:
    fig_height: 3
    fig_width: 8
    reference_docx: epi_template.docx
  pdf_document: default
  html_document: default
params:
  organism:
    label: "Organism"
    input: text
    value: "COVID-19 (SARS-CoV-2)"
  response:
    label: "Response type"
    input: text
    value: "standard national"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, error=FALSE)
options(knitr.kable.NA = "Unknown")
```

```{r load libraries/functions, include=FALSE, message = FALSE}
pkgs <- c('tidyverse'	,'lubridate'	,'readxl'	,'epitrix'	,'dplyr'	,'kableExtra'	,'EpiCurve'	,'epitools'	,'flextable'	,'officer'	,'coarseDataTools'	,'janitor'	,'here'	,'googlesheets4'	,'purrr'	,'scales'	,'linelist'	,'tidyr'	,'plotrix'	,'tsibble'	,'tmap'	,'here'	,'purrr'	,'linelist'	,'ggthemes'	,'gt'	,'RcppRoll'	,'scales'	,'patchwork'	,'flexdashboard'	,'googlesheets4','table1'	,'ggpubr'	,'tmap'	,'htmltools'	,'magrittr'	,'mapproj'	,'sf'	,'ggplot2', 'glue')
pacman::p_load(pkgs, character.only = T)
source(here('code','modules', '0_setup.R'))
```

```{r core_processing, include=FALSE, message = FALSE}
source(here('code','modules',"01_all.R"))
```


::: {custom-style="subtitle"}
`r params$subtitle`
:::

::: {custom-style="centre"}
`r params$date`
:::


```{r, child=c(here::here("code","rmds","1_introduction.Rmd"), here::here("code","rmds","2_exec_summary.Rmd"))}
```

# Summary of cases - week `r LastWeek` and week `r ThisWeek`

-   There have been **`r cases_week_camp %>% filter(week==ThisWeek) %>% ungroup() %>%  summarise(cases=sum(cases,na.rm=TRUE)) %>% pull(cases)`** new cases in the FDMN/Rohingya Refugee population in week `r ThisWeek`. In week `r LastWeek` there were **`r cases_week_camp %>% filter(week==LastWeek) %>% ungroup() %>%  summarise(cases=sum(cases,na.rm=TRUE)) %>% pull(cases)`** cases.

## Age of cases

-   The median age of the cases this week (week `r ThisWeek`) was `r MedianAgeThisWeek` years old.
-   The median age of the cases last week (week `r LastWeek`) was `r MedianAgeLastWeek` years old.

## Sex breakdown

-   This week (week `r ThisWeek`) there were **`r ThisWeekMale`** male (`r Male_Prop_ThisWeek`%) and **`r ThisWeekFemale`** female (`r Female_Prop_ThisWeek`%) cases.
-   Last week (week `r LastWeek`) there were **`r LastWeekMale`** male (`r Male_Prop_Week`%) and **`r LastWeekFemale`** female (`r Female_Prop_Week`%) cases.

## Location of cases

-   The following camps reported cases in week `r LastWeek` or `r ThisWeek`

```{r}
cases_tests_table
```

## Testing - week `r LastWeek` & `r ThisWeek`

-   This week (week `r ThisWeek`), **`r camp_test_fortnight %>% filter(week==ThisWeek) %>%  pull(total_tests)`** samples were tested. Last week (week `r LastWeek`), **`r camp_test_fortnight %>% filter(week==LastWeek) %>%  pull(total_tests)`** samples were tested.

-   This week (week `r ThisWeek`), **`r camp_test_fortnight %>% filter(week==ThisWeek) %>%  pull(positivity)`** of samples were positive for COVID-19. Last week (week `r LastWeek`), **`r camp_test_fortnight %>% filter(week==LastWeek) %>%  pull(positivity)`** of samples were positive for COVID-19.

# Descriptive epidemiology - FDMN/Rohingya refugee cases

-   The first test in the FDMN/Rohingya population was on `r first_test_fdmn_day_month` (Week `r first_test_fdmn_week`).
-   The first confirmed case in the FDMN/Rohingya population was on `r first_case_fdmn_day_month` (Week `r first_case_fdmn_week`).

## Age and sex breakdown

-   The overall median age of cases is **`r medianage`** (range **`r RangeLow` - `r RangeUpper`** years old).
-   There have been **`r Male`** (`r Male_Prop`%) male cases and **`r Female`** (`r Female_Prop`%) female cases.

<br> <br>

```{r, fig.cap="Figure 2: Confirmed cases by week and sex (FDMN/ Rohingya Refugees)"}
EpicurveSex
```

<br> <br>

### Age and sex pyramid - confirmed cases FDMN/Rohingya refugee

```{r ageandsexplot, fig.cap="Figure 3: Confirmed cases by age group and sex (FDMN/ Rohingya Refugees)", echo=FALSE, warning=FALSE, message=FALSE}
AgeSex
```

### Cases per 100,000 by age group

```{r}
cases_agegrp
```

## Severity of reported cases at presentation

<br>

```{r, fig.cap="Table 2: Cases by severity of disease at presentation (FDMN/ Rohingya Refugees)"}
case_severity
```

<br>

<br>

```{r, fig.cap="Figure 4: Case severity at presentation by week (FDMN/ Rohingya Refugees)"}
SeverityEpicurve
```

<br>

## Outcomes at 30 days

As of Week **`r ThisWeek`** there have been **`r deathscount`** deaths in the FDMN/Rohingya Refugee population from COVID-19.

<br> <br>

```{r}
severity_outcome
```

<br> <br>

## Location of cases and cases per 100,000

-   As of this week (week `r ThisWeek`), **`r CampsWithCases`**/34 camps have confirmed cases.The number of cases per 100,000 people for each camp is displayed on a map in the Appendix.

# Testing

## Positivity

-   Between Week **`r first_test_fdmn_week`** & Week **`r ThisWeek`**, **`r FDMN_Test`** samples have been tested from the FDMN/Rohingya Refugee population since.

-   `r n_cases_FDMN` **(`r FDMNOverallPosNum`)%** samples have been positive for COVID-19.

<br>

```{r, fig.cap="Figure 5: Tests and cases by week"}
FDMN_Test_graph
```

<br>

## Age of samples tested

-   Overall, the median age of samples tested is `r tests_age_overall$median` years old.
-   This week (week `r ThisWeek`) the median age of samples tested was `r tests_age_thisweek$median` years old.
-   Last week (week `r LastWeek`) the median age of samples tested was `r tests_age_lastweek$median` years old.

```{r tests_by age , fig.cap="Figure 6: Age of samples tested by week"}
tests_age_gph
```

## Location of tests

The number of tests per 100,000 people for each camp is displayed on a map in the Appendix.

\newpage

```{r, child=c(here::here("code","rmds","6_further_info.Rmd"))}
```


```{r, child=c(here::here("code","rmds","7_appendix.Rmd"))}
```