# Descriptive epidemiology - FDMN/Rohingya refugee cases

-   The first test in the FDMN/Rohingya population was on `r first_test_fdmn_day_month` (Week `r first_test_fdmn_week`).
-   The first confirmed case in the FDMN/Rohingya population was on `r first_case_fdmn_day_month` (Week `r first_case_fdmn_week`).

## Age and sex breakdown

-   The overall median age of cases is **`r medianage`** (range **`r RangeLow` - `r RangeUpper`** years old).
-   There have been **`r Male`** (`r Male_Prop`%) male cases and **`r Female`** (`r Female_Prop`%) female cases.

<br> <br>

```{r, fig.cap="Figure 2: Confirmed cases by week and sex (FDMN/ Rohingya Refugees)"}

summary_Sex <- FDMN_Only2 %>% 
  mutate(yearweek=yearweek(date_of_case_detection)) %>% 
  count(yearweek, sex) %>% 
  mutate(sex=case_when(sex=='M' ~ 'Male',
                       sex=='F' ~ 'Female'))

EpicurveSex<-
  ggplot(summary_Sex, aes(x=yearweek, y=n, fill=sex)) +
  geom_col() +
  theme_minimal() +
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) + 
    scale_fill_brewer(palette="Dark2", direction=-1) +
      #scale_x_continuous(breaks=breaks_pretty(n = 8)) +
    scale_x_yearweek(date_breaks = "4 week",) +
  labs(x = "Week", y = "Number of cases", fill='') +
  #ggtitle("Figure 2: Confirmed cases by specimen collection week (FDMN/ Rohingya Refugees) by sex") + 
  theme(plot.title = element_text(size=10))
  #scale_fill_discrete(name="")

EpicurveSex

```

<br> <br>

### Age and sex pyramid - confirmed cases FDMN/Rohingya refugee

```{r ageandsexplot, fig.cap="Figure 3: Confirmed cases by age group and sex (FDMN/ Rohingya Refugees)", echo=FALSE, warning=FALSE, message=FALSE}

# AgeSex_df <- FDMN_Only %>%  mutate(sex=case_when(sex=='M' ~ 'Male',
#                        sex=='F' ~ 'Female'))
# AgeSex<- AgeSex_df %>% 
#     mutate(age_grp=cut(age_in_years, breaks=c(-Inf,18,59, +Inf), 
#                        labels=c('Under 18', '18 to 59' ,'60 and over'))) %>% 
# ggplot(.,aes(x=age_grp, fill=sex)) +
#             geom_bar(data=subset(AgeSex_df,sex=="Female"), color="white", width=1) +
#             geom_bar(data=subset(AgeSex_df,sex=="Male"), aes(y=..count..*(-1)), color="white", width=1) +
#             theme_minimal() +
#             labs(x='Age group', y='Number of cases') +
#             scale_y_continuous(breaks=seq(-48,48,8),labels=abs(seq(-48,48,8))) +
#             #scale_x_discrete(limits=levels(.$agerp)) +
#             geom_hline(yintercept=0) +
#       scale_fill_brewer(palette="Dark2", direction=-1) +
#             coord_flip() +
#            theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), legend.title=element_blank())

FDMN_df <- FDMN_Only2 %>%  mutate(sex=case_when(sex=='M' ~ 'Male',
                                                   sex=='F' ~ 'Female')) %>% 
    mutate(age_grp=cut(age_in_years, breaks=c(-Inf,18,59, +Inf), 
                       labels=c('Under 18', '18 to 59' ,'60 and over')))

AgeSex <-    ggplot(FDMN_df,aes(x=age_grp, fill=sex)) +
    geom_bar(data=subset(FDMN_df,sex=="Female"), color="white", width=1) +
    geom_bar(data=subset(FDMN_df,sex=="Male"), aes(y=..count..*(-1)), color="white", width=1) +
    theme_minimal() +
    labs(x='Age group', y='Number of cases') +
    scale_y_continuous(breaks=seq(-100,100,10),labels=abs(seq(-100,100,10))) +
    #scale_x_discrete(limits=levels(.$agerp)) +
    geom_hline(yintercept=0) +
    scale_fill_brewer(palette="Dark2", direction=-1) +
    coord_flip() +
    theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank(), legend.title=element_blank())
  

AgeSex
```

### Cases per 100,000 by age group

```{r}
population_agegrp <- readxl::read_xlsx(here('data','block_population.xlsx'), sheet='Final', skip=1) %>% 
  clean_names %>%  
  clean_data() %>% 
  filter(grepl('total', camp)) %>% 
  filter(!camp=='grand_total') %>% 
  select(-block) %>% 
  mutate(across(c(infant_below_1:x16), as.numeric)) %>% 
  mutate(age_0_18 = rowSums(.[4:11])) %>% 
  mutate(age_18_59 = rowSums(.[12:13])) %>% 
  mutate(age_over60 = rowSums(.[14:15])) %>% 
  select(camp, contains('total'), contains('age')) %>% 
  mutate(camp=gsub('_total', '', camp)) %>% 
  mutate(camp=gsub('camp_', '', camp)) %>% 
  mutate(camp=trimws(camp))  %>% 
  select(camp, contains('age')) %>% 
  summarise(age_0_18=sum(age_0_18,na.rm=TRUE),
            age_18_59=sum(age_18_59,na.rm=TRUE),
            age_over60=sum(age_over60,na.rm=TRUE)) %>% 
  mutate(dummy=1) %>% 
  pivot_longer(-dummy) %>% 
  mutate(age_grp=case_when(name=='age_0_18' ~ 'Under 18',
                        name=='age_18_59' ~ '18 to 59',
                        name=='age_over60' ~ '60 and over')) %>% 
  select(-c(dummy,name))

cases_agegrp <- FDMN_Only2 %>% 
  mutate(age_grp=cut(age_in_years, breaks=c(-Inf,18,59, +Inf), labels=c('Under 18', '18 to 59' ,'60 and over'))) %>% 
#  mutate(week=isoweek(date_of_case_detection)) %>% 
   mutate(yearweek=yearweek(date_of_case_detection)) %>% 
  count(yearweek,age_grp, .drop=FALSE) %>% 
  left_join(population_agegrp, by='age_grp') %>% 
  mutate(per_capita=(n/value)*100000) %>% 
  mutate(age_grp=factor(age_grp, levels=c('Under 18', '18 to 59', '60 and over'))) %>% 
  ggplot(., aes(x=yearweek,y=per_capita, fill=age_grp)) +
  geom_col(width = 3) +
  theme_minimal() +
      scale_fill_brewer(palette="Dark2", direction=-1) +
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) +
      #scale_x_continuous(breaks=breaks_pretty(n = 8)) +
      scale_x_yearweek(date_breaks = "4 week") +
    labs(x="Week", y="Cases 100,000 people", fill='Age group')

cases_agegrp

```

## Severity of reported cases at presentation

<br>

```{r, fig.cap="Table 2: Cases by severity of disease at presentation (FDMN/ Rohingya Refugees)"}
Summary_Severity<- FDMN_Only2 %>%
  mutate(severity_of_disease=factor(severity_of_disease, levels=c('Critical', 'Severe', 'Mild/Moderate', 'Asymptomatic', 'Unknown'))) %>% 
  group_by(severity_of_disease) %>%
  summarise(count=n()) %>% 
    adorn_totals(where=c('row')) %>% 
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns() 

# Summary_Severity<- Summary_Severity%>%
#   adorn_totals("row")
# 
# Proportions<-round(Summary_Severity$count/ n_cases_FDMN *100, 1)
# Summary_Severity['Percentage'] = Proportions

Summary_Severity_Flex<-flextable(Summary_Severity)

Table1<-Summary_Severity_Flex %>%
set_header_labels(severity_of_disease = "Severity of Disease",
                  count = "Frequency",
                  Percentage = "Percentage of total (%)") %>%
bold(bold = TRUE, part = "header")
Table1<-autofit(Table1)
Table1<- fontsize(Table1, size = 10, part="all") 

Table1 %>% 
    add_header_lines(., values = "Table 2: Cases by severity of disease at presentation")


```

<br>

<br>

```{r, fig.cap="Figure 4: Case severity at presentation by week (FDMN/ Rohingya Refugees)"}
# Epidemic curve by severity

#summary_severity <- as.data.frame(aggregate(FDMN_Only$count, by = list(FDMN_Only$Week, FDMN_Only$severity_of_disease), FUN =sum))

summary_severity <- FDMN_Only2 %>%   mutate(yearweek=yearweek(date_of_case_detection)) %>% 
    count(yearweek, severity_of_disease) %>% 
  mutate(severity_of_disease=ifelse(is.na(severity_of_disease), 'Unknown',severity_of_disease))


SeverityEpicurve<-
  ggplot(summary_severity, aes(x=yearweek, y=n, fill=factor(severity_of_disease, levels=c('Critical', 'Severe', 'Mild/Moderate', 'Asymptomatic', 'Unknown')))) +
  geom_col(position="stack") +
  theme_minimal() +
        scale_fill_brewer(palette="Dark2") +
    #scale_fill_manual(values=c("yellow", "red", "forest green", "dark orange", "dark grey")) +
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) +
      #scale_x_continuous(breaks=breaks_pretty(n = 8)) +
      scale_x_yearweek(date_breaks = "4 week",) +
  labs(x = "Week", y = "Number of cases", fill='Severity of disease at presentation') 
  #ggtitle("Figure 3: Confirmed cases last week by severity (FDMN/ Rohingya Refugees)") + theme(plot.title = element_text(size=10))

SeverityEpicurve

EpicurveSex<-
  ggplot(summary_Sex, aes(x=yearweek, y=n, fill=sex)) +
  geom_col() +
  theme_minimal() +
  theme(panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) + 
    scale_fill_brewer(palette="Dark2", direction=-1) +
      #scale_x_continuous(breaks=breaks_pretty(n = 8)) +
    scale_x_yearweek(date_breaks = "4 week",) +
  labs(x = "Week", y = "Number of cases", fill='') +
  #ggtitle("Figure 2: Confirmed cases by specimen collection week (FDMN/ Rohingya Refugees) by sex") + 
  theme(plot.title = element_text(size=10))
  #scale_fill_discrete(name="")
```

<br>

## Outcomes at 30 days

As of Week **`r ThisWeek`** there have been **`r deathscount`** deaths in the FDMN/Rohingya Refugee population from COVID-19.

<br> <br>

```{r}

#Sum_tab_Severity<-as.data.frame(table(FDMN_Only$`30_day_outcome`, FDMN_Only$severity_of_disease))


Sum_tab_Severity <- FDMN_Only2 %>% 
  mutate(severity_of_disease=factor(severity_of_disease, levels=c('Critical', 'Severe', 'Mild/Moderate', 'Asymptomatic', 'Unknown'))) %>% 
  clean_names() %>% 
  tabyl(severity_of_disease,x30_day_outcome) %>% 
   adorn_totals(where=c('row', 'col')) %>% 
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1) %>%
  adorn_ns() %>% 
  rename('Disease severity'=severity_of_disease)

#names(Sum_tab_Severity) <- c('Outcome at 30 days', 'Severity of disease','count')


# Sum_tab_Severity <- Sum_tab_Severity %>% 
#   pivot_wider(names_from='Outcome at 30 days', values_from=count, values_fill = 0)


Sum_tab_Severity2<-flextable(Sum_tab_Severity)
Sum_tab_Severity2<-autofit(Sum_tab_Severity2)
Sum_tab_Severity2<- fontsize(Sum_tab_Severity2, size = 10, part="all") %>% 
  bold(bold = TRUE, part = "header")



# DeathsAsymp<-Sum_tab_Severity[1,2]
# DeatsCritical <-Sum_tab_Severity[2,2]
# DeathsSevere<-Sum_tab_Severity[4,2]
# DeathsMildModerate	<-Sum_tab_Severity[3,2]
# DeathsUnknown<-Sum_tab_Severity[5,2]

Sum_tab_Severity2  %>% 
      add_header_lines(., values = "Table 3: Cases by severity of disease at presentation & 30-day outcome")

```

<br> <br>

## Location of cases and cases per 100,000

-   As of this week (week `r ThisWeek`), **`r CampsWithCases`**/34 camps have confirmed cases.The number of cases per 100,000 people for each camp is displayed on a map in the Appendix.

```{r}
CasesCampTable<-CasesCamp[order(-CasesCamp$count), ]

CasesCampTable<-flextable(CasesCampTable)
CasesCampTable<-autofit(CasesCampTable)

# Number of cases by camp
CasesCamp<- FDMN_Only2 %>%
  group_by(camp_of_residence) %>%
  summarise(count=n()) %>% 
  mutate(camp_of_residence=as.character(camp_of_residence))

# Remove the word "camp" from the population data to allow merges
population<-population %>%
  mutate(camp_of_residence = gsub("Camp", "", New_Camp_Name))

#triming white space in the dataframe
population$camp_of_residence<-trimws(population$camp_of_residence, which = c("both", "left", "right"), whitespace = "[ \t\r\n]")

#Merge the CasesCamp and Population data together
TablePop<- left_join(population, CasesCamp, by="camp_of_residence")

#Generate the rates per 100,000 and add to the Table Pop dataframe
Ratesper100k<-round(TablePop$count/TablePop$Total_Pop*100000, 1)
TablePop$Ratesper100k<-Ratesper100k

#Sort from high to low based on rates per 100,000
TablePopOrdered<-TablePop[order(TablePop$Ratesper100k, na.last= TRUE, decreasing = TRUE),]


```

```{r Map}
source(here('modules',"05 - Maps.R"))

cases_map <-    Map_Rates100kData %>% 
  mutate(camp_label=gsub('Camp ', '', New_Camp_Name)) %>% 
  mutate(camp_label=gsub('Extension', 'E', camp_label)) %>% 
  mutate(upazila_upd=case_when(camp_label %in% c('21','22','23') ~ 'Teknaf North',
                               camp_label %in% c('24', '25', '26', '27', 'Nayapara RC') ~ 'Teknaf South',
                               TRUE ~ Upazila)) %>% 
   mutate(upazila_upd=factor(upazila_upd, levels=c('Ukhia', 'Teknaf South', 'Teknaf North'))) %>% 
  filter(!is.na(Upazila)) %>% 
  tm_shape() +
  tm_polygons("Ratesper100k", title="Cases per 100,000", palette="YlGn",textNA = "No reported cases") +
  tm_facets(by="upazila_upd", nrow=2) +
  #tm_text("camp_label", fontface = "bold") +
  tm_borders()
  
tests_map <- Map_Tests100kData %>% 
  mutate(camp_label=gsub('Camp ', '', New_Camp_Name)) %>% 
    mutate(camp_label=gsub('Extension', 'E', camp_label)) %>% 
  mutate(upazila_upd=case_when(camp_label %in% c('21','22','23') ~ 'Teknaf North',
                               camp_label %in% c('24', '25', '26', '27', 'Nayapara RC') ~ 'Teknaf South',
                               TRUE ~ Upazila)) %>% 
   mutate(upazila_upd=factor(upazila_upd, levels=c('Ukhia', 'Teknaf South', 'Teknaf North'))) %>% 
  filter(!is.na(Upazila)) %>% 
  tm_shape() +
  tm_polygons("tests100k", title="Tests per 100,000", palette="BuPu",textNA = "No reported tests") +
  tm_facets(by="upazila_upd", nrow=2) +
  #tm_text("camp_label",  fontface = "bold") +
  tm_borders()

```
