# Testing

```{r,warnings=FALSE}
library(ggplot2)
library(lubridate)

# test_nationality<-test_nationality %>%
#   mutate(date_test = ymd(test_nationality$date_format))

# Graph for testing the FDMN population

FDMN_Test_graph<-test_nationality %>% 
  filter(name %in% c('fdmn', 'fdmn_positive')) %>% 
  mutate(week=isoweek(date_format)) %>% 
  mutate(year=year(date_format)) %>% 
  filter(week <= ThisWeek | year==2020) %>% 
  mutate(yearweek=yearweek(date_format)) %>% 
  select(yearweek,name,value) %>% 
  group_by(yearweek,name) %>% 
  summarise(value=sum(value,na.rm=TRUE)) %>% 
  mutate(name_fac=factor(name, levels = c('fdmn', 'fdmn_positive'),
                         labels=c('Tests', 'Cases'))) %>% 
  ggplot(., aes(x=yearweek, y=value, fill=name_fac)) +
  geom_bar(stat="identity") +
      scale_fill_manual(values=c("#ED7D31","#4472C4")) +
      scale_x_yearweek(date_breaks = "8 week",) +
#      scale_x_continuous(breaks=breaks_pretty(n = 8)) +
  # scale_x_date(date_breaks= '30 day', date_minor_breaks = '7 day',
  #              date_labels = '%d-%m') +
  labs(caption = "Data source: Cox’s Bazar - IEDCR Field Lab",
       x="Week",
       y= "Number",
       fill="") +
  theme_minimal()


```

## Positivity

```{r, include=FALSE}


#Making a % positive
FDMNPos<- TestingClean[, c(1,4,5)]
FDMNPos$Positivity<-round(FDMNPos$fdmn_positive/FDMNPos$fdmn*100, 1)

FDMNOverallPos<- FDMNPos %>%
  summarise(total_tests = sum(fdmn, na.rm=TRUE),
             total_cases = sum(fdmn_positive, na.rm=TRUE)) %>%
              mutate(Overall_Pos = round(as.numeric(total_cases/total_tests*100), 1))

FDMNOverallPosNum<-FDMNOverallPos$Overall_Pos

FDMNPos$date<-as.Date(FDMNPos$date)

```

-   Between Week **`r first_test_fdmn_week`** & Week **`r ThisWeek`**, **`r FDMN_Test`** samples have been tested from the FDMN/Rohingya Refugee population since.

-   `r n_cases_FDMN` **(`r FDMNOverallPosNum`)%** samples have been positive for COVID-19.

<br>

```{r, fig.cap="Figure 5: Tests and cases by week"}

FDMN_Test_graph
```

<br>

## Age of samples tested

-   Overall, the median age of samples tested is `r tests_age_overall$median` years old.
-   This week (week `r ThisWeek`) the median age of samples tested was `r tests_age_thisweek$median` years old.
-   Last week (week `r LastWeek`) the median age of samples tested was `r tests_age_lastweek$median` years old.

```{r tests_by age , fig.cap="Figure 6: Age of samples tested by week"}

tests_age_gph
```

## Location of tests

The number of tests per 100,000 people for each camp is displayed on a map in the Appendix.

\newpage