

# Further information

## Case definitions

### Suspected COVID-19

A. Person who meets the clinical AND epidemiological criteria:

-   Clinical criteria:

    Acute onset of fever AND cough; OR,

    Acute onset of ANY THREE OR MORE of the following signs or symptoms:

    -   fever,cough

    -   general weakness/fatigue

    -   headache

    -   myalgia

    -   sore throat

    -   coryza

    -   dyspnoea

    -   anorexia/nausea/vomiting

    -   diarrhoea

    -   altered mental status.

-   Epidemiological criteria

    -   Residing (or working) in an area with high risk of transmission of the virus: for example, closed residential settings and humanitarian settings, such as camp and camp-like settings for displaced persons, any time within the 14 days prior to symptom onset;

        OR,

    -   Residing in or travel to an area with community transmission anytime within the 14 days prior to symptom onset;

        OR,

    -   Working in health setting, including within health facilities and within households, anytime within the 14 days prior to symptom onset.

B. A patient with severe acute respiratory illness (SARI: acute respiratory infection with history of fever or measured fever of ≥ 38 C°; and cough; with onset within the last 10 days; and who requires hospitalization)

### Probable COVID-19

Definition A: A patient who meets clinical criteria above AND is a contact of a probable or confirmed case, or epidemiologically linked to a cluster of cases which has had at least one confirmed case identified within that cluster.

Definition B: A suspected case (described above) with chest imaging showing findings suggestive of COVID-19 disease.

Definition C: A person with recent onset of anosmia (loss of smell) or ageusia (loss of taste)in the absence of any other identified cause.

Definition D: Death, not otherwise explained, in an adult with respiratory distress preceding death AND who was a contact of a probable or confirmed case or epidemiologically linked to a cluster which has had at least one confirmed case identified within that cluster.

### Confirmed COVID-19

A person with laboratory confirmation of COVID-19 infection, irrespective of clinical signs and symptoms.

\newpage

#### Appendix 1 - Tests & cases in Cox's Bazar host population

```{r}

Host_Test_graph <- test_nationality %>% 
  filter(name %in% c('host', 'host_positive')) %>% 
  mutate(week=isoweek(date_format)) %>% 
    mutate(year=year(date_format)) %>% 
  select(year,week,name,date_format,value) %>% 
  filter(week <= ThisWeek | year==2020) %>% 
  mutate(yearweek=yearweek(date_format)) %>% 
  group_by(yearweek,name) %>% 
  summarise(value=sum(value,na.rm=TRUE)) %>% 
  mutate(name_fac=factor(name, levels = c('host', 'host_positive'),
                         labels=c('Tests', 'Cases'))) %>% 
  ggplot(., aes(x=yearweek, y=value, fill=name_fac)) +
  geom_bar(stat="identity") +
    scale_fill_manual(values=c("#ED7D31","#4472C4")) +
        scale_x_yearweek(date_breaks = "8 week",) +
      #scale_x_continuous(breaks=breaks_pretty(n = 8)) +
 # scale_x_continuous(limits=c(10,ThisWeek)) +
  # scale_x_date(date_breaks= '30 day', date_minor_breaks = '7 day',
  #              date_labels = '%d-%m') +
  labs(caption = "Data source: Cox’s Bazar - IEDCR Field Lab",
       x="Week",
       y= "Number",
       fill="") +
  theme_minimal()



Host_Test_graph
```

#### Appendix 2 - Tests & cases in Bangladesh

```{r}

#Bangladesh data from Our World In Data
bgd_data <- read.csv('https://covid.ourworldindata.org/data/owid-covid-data.csv') %>% 
  filter(iso_code=='BGD') %>%        
  mutate(date_format=ymd(date)) %>% 
  select(date=date_format, new_tests,new_cases,new_deaths,population) %>% 
  mutate(population_group='Bangladesh') %>% 
    mutate(week=isoweek(date)) %>% 
    mutate(year=year(date)) %>% 
  #select(year,week,name,date_format,value) %>% 
  filter(week <= ThisWeek | year==2020) %>% 
  mutate(yearweek=yearweek(date)) 
  #mutate(week=isoweek(date)) %>% 
  #filter(week<=ThisWeek)

bgd_graph <- bgd_data %>% 
  select(yearweek, new_cases, new_tests) %>% 
  group_by(yearweek) %>% 
  summarise(cases=sum(new_cases,na.rm=TRUE),
            tests=sum(new_tests,na.rm=TRUE)) %>% 
  pivot_longer(-yearweek) %>% 
  mutate(name_fac=factor(name, levels = c('tests', 'cases'),
                         labels=c('Tests', 'Cases'))) %>% 
  ggplot(., aes(x=yearweek, y=as.numeric(value), fill=name_fac)) +
  geom_bar(stat="identity") +
      scale_fill_manual(values=c("#ED7D31","#4472C4")) +
          scale_x_yearweek(date_breaks = "8 week",) +
     # scale_x_continuous(breaks=breaks_pretty(n = 8)) +
  # scale_x_date(date_breaks= '30 day', date_minor_breaks = '7 day',
  #              date_labels = '%d-%m', limits=c(ymd('2020-03-17'), today())) +
  labs(caption = "Data source: IEDCR (https://covid19bd.idare.io/)",
       x="Week",
       y= "Number",
       fill="") +
  theme_minimal()

bgd_graph  
```

\newpage

#### Appendix 3 - Cases per 100,000 by household location

```{r, fig.height=10}
cases_map
```

\newpage

#### Appendix 4 - Tests per 100,000 by household location

```{r, fig.height=10}
tests_map

```
